---
title: "Final Project: Game Sales Analysis"
author: 'Puttisan "Ninja" Mukneam'
date: "05/13/2022"
output:
   pdf_document: default
---

```{r, message=FALSE}
#Loading the Libraries
library(tidyverse)
library(lubridate)
library(modelr)
library(ggplot2)
library(partykit)
options(na.action = na.warn)
knitr::opts_chunk$set(dev = 'pdf')
```

```{r, message=FALSE}
#importing data
steam_data_1 <- read_csv("steam_data.csv") #w/o game's genre
steam_data_2 <- read_csv("steam.csv") # w game's genre
steam_game_popularity <- read_csv("SteamCharts.csv")
twitch_game_popularity <- read_csv("Twitch_game_data.csv")
video_game_sales_1 <- read_csv("video_gamesgit.csv")
video_game_sales_2 <- read_csv("Video_Games (2).csv")
```

--------------------------------Delete--------------------------------

## Question 1 (18 points)


> **Consider the data Ca-Vac-Jan-Jun.csv.  On the last homework, we fit this data with a quadratic and a quartic model. Now, we'll try splines! **

> a. (3 points) **Create a model for this data that is a spline with one degree of freedom.  Make predictions for your model, and draw your model on top of the data points.  What do you observe?**

--------------------------------Delete--------------------------------

Questions to answer

- What is the most popular genre, in term of the number of players, over the available data period, and how genres has change over time.
- Can we have a model predicting global sales of a game using its genre, developer and critic score.
- Are there any relationship between critics score and player review (ratio of a game?)
- Are there any relationship between Twitch's viewer and global sale of a game?

--------------------------------Delete--------------------------------


## Question 1: What is the most popular genre, in term of the number of players, over the available data period, and how genres has change over time.

> **Cleaning relevant data**

> a. **steam_data_1**

```{r, message=FALSE}
#Cleaning dates
steam_data_1_cleaned_1 <- steam_data_1 %>%
  #filtering out duplicate rows with same names and same developers
  distinct(name, developer, .keep_all = TRUE) %>% 
  select(date, name, developer) %>%
  filter(!is.na(name),
         !name == "-",
         !date == "-",
         #filtering out non-date value
         !str_detect(date, "\\w{3}", negate = TRUE)) %>% 
  rename(game_name = name,
         release_date = date) %>%
  mutate(release_date = parse_date_time(release_date, orders = c("%b %d, %Y", 
                                                                 "%d %b, %Y",
                                                                 "%m/%d/%Y",
                                                                 "%Y/%m/%d",
                                                                 "%Y-%m-%d",
                                                                 "%d.%m.%Y",
                                                                 "%m.%d.%Y"))) %>%
  filter(!is.na(release_date))


#Cleaning developer
steam_data_1_cleaned_2 <- steam_data_1_cleaned_1 %>%
  mutate(temp_dev = str_split(developer,
                        ", (?!L(?i)t(?i)d(?i).?|L(?i)C(?i)C(?i).?|I(?i)n(?i)c(?i).?|L(?i).?L(?i).?C(?i).?|.dat|s. r. o.)")) %>%
  # From this line, we are separating each developer into multiple columns
  unnest_legacy(temp_dev) %>%               
  group_by(developer, game_name) %>%
  mutate(temp_id = row_number()) %>%
  pivot_wider(names_from = temp_id,
              values_from = temp_dev,
              names_prefix = "developer_") %>%
  ungroup() %>%
  select(-developer) 
```

> b. **steam_data_2**

```{r}
#Cleaning genres
steam_data_2_cleaned_1 <- steam_data_2 %>%
  #filtering out duplicate rows with same names and same developers
  distinct(name, developer,.keep_all = TRUE) %>% 
  select(name, genres, developer) %>%
  #I do not think that Early Access counts as game genre. 
  #So we are excluding them here
  filter(genres != "Early Access") %>%          
  rename(game_name = name) %>%
  mutate(genres = ifelse(str_detect(genres, ";Early Access"),
                         str_remove(genres, ";Early Access"),
                         str_remove(genres, "Early Access;"))) %>%
  mutate(temp_genres = str_split(genres, ";")) %>%
  # From this line, we are separating each developer into multiple columns
  unnest_legacy(temp_genres) %>%
  group_by(developer, game_name) %>%
  mutate(temp_id = row_number()) %>%
  pivot_wider(names_from = temp_id,
              values_from = temp_genres,
              names_prefix = "genre_") %>%
  ungroup() %>%
  select(- genres)

#Cleaning developer
steam_data_2_cleaned_2 <- steam_data_2_cleaned_1 %>%
  mutate(temp_dev = ifelse(str_detect(developer, ";"),
                           str_split(developer, ";"),
                           str_split(developer,
                                     ", (?!L(?i)t(?i)d(?i).?|L(?i)C(?i)C(?i).?|I(?i)n(?i)c(?i).?|L(?i).?L(?i).?C(?i).?|.dat|s. r. o.)"))) %>%
  # From this line, we are separating each developer into multiple columns
  unnest_legacy(temp_dev) %>%
  group_by(developer, game_name) %>%
  mutate(temp_id = row_number()) %>%
  pivot_wider(names_from = temp_id,
              values_from = temp_dev,
              names_prefix = "developer_") %>%
  ungroup() %>%
  select(-developer)
```

> c. **Joining tibbles**

```{r}
#Preparing columns to join with steam_data_1
steam_data_2_cleaned_2_joinable <- steam_data_2_cleaned_2 %>%
  #low-casing and removing all special characters
  mutate(joined_game_name = str_replace_all(game_name, "[^[:alnum:] ]", " "),
         joined_game_name = str_to_lower(joined_game_name),
         #Using at most 2 developers as a joined column
         joined_dev = ifelse(is.na(developer_2),
                             developer_1,
                             str_c(developer_1, developer_2, sep = " ")),
         joined_dev = str_replace_all(joined_dev, "[^[:alnum:] ]", " "),
         joined_dev = str_to_lower(joined_dev)) %>%
  select(genre_1:genre_16, joined_game_name, joined_dev)

#Preparing columns to join with steam_data_2 and joining them
steam_data_1_with_genres <- steam_data_1_cleaned_2 %>%
  #preparing joined columns
  mutate(joined_game_name = str_replace_all(game_name, "[^[:alnum:] ]", " "),
         joined_game_name = str_to_lower(joined_game_name),
         joined_dev = ifelse(is.na(developer_2),
                             developer_1,
                             str_c(developer_1, developer_2, sep = " ")),
         joined_dev = str_replace_all(joined_dev, "[^[:alnum:] ]", " "),
         joined_dev = str_to_lower(joined_dev)) %>%
  select(release_date, game_name, joined_game_name, joined_dev) %>%
  filter(!is.na(joined_dev)) %>%
  #joining using inner_join so that we can work with games that have their 
  #genres recorded
  inner_join(steam_data_2_cleaned_2_joinable, 
                       by = c("joined_game_name", "joined_dev"))

#Cleaning and Preparing columns to join with steam_data_1_with_genres
steam_game_pop_joinable <- steam_game_popularity %>%
  mutate(year = as.integer(year),
         joined_game_name = str_replace_all(gamename, "[^[:alnum:] ]", " "),
         joined_game_name = str_to_lower(joined_game_name)) %>%
  select(gamename, year, month, avg, joined_game_name) %>%
  #Excluding year 2021 because there are only recordings from Jan and Feb
  filter(!year == 2021)


#Preparing columns to join with steam_game_pop_joinable
steam_data_1_with_1_genre <- steam_data_1_with_genres %>%
  #Pivot games' genres into rows so that we look at every genre instead of 
  #only 1 genre and with a bunch of NAs, which will produce greater complexity
  pivot_longer(genre_1:genre_16, names_to = "genre", values_drop_na = TRUE) %>%
  select(- genre) %>%
  rename("genres" = value)


#joining steam_game_pop_joinable and steam_data_1_with_1_genre to achieve a
#tibble to answer question 1
q1 <- inner_join(steam_game_pop_joinable, steam_data_1_with_1_genre, by = "joined_game_name") %>%
  select(-joined_game_name, - gamename)

q1
```


> **Answering question**

> a. **genres vs time**Delete maybe


```{r, fig.height=7}
#average by year
#Collapsing all the months of that year by taking their average
 q1_avg_by_year <- q1 %>%
   group_by(year, genres) %>%
   summarise(avg_by_genre = mean(avg)) %>%
   ungroup()

#plot
q1_avg_by_year %>%
  ggplot() + 
  geom_point(aes(x = year,
                 y = avg_by_genre,
                 color = genres),
             size = 3) +
  theme(text = element_text(size = 15),
        legend.position = "bottom",
        legend.title = element_text(size = 10), 
        legend.text = element_text(size = 10)) 
  


#table Top-1 each year
q1_avg_by_year %>%
  group_by(year) %>% 
  filter(avg_by_genre == max(avg_by_genre)) 
```

```{r}
#anlsys

q1 %>%
  filter(year == 2020, genres == "Free to Play") %>%
  arrange(desc(avg))
```
```{r}
#Top- 3
q1_avg_by_year %>%                       
  arrange(desc(avg_by_genre)) %>% 
  group_by(year) %>%
  slice(1:3) %>%
  ggplot() + 
  geom_point(aes(x = year,
                 y = avg_by_genre,
                 color = genres),
             size = 5,
             alpha = 0.6)
```



## Question 2:Are there any relationship between critics score and player review (ratio of a game?)

> **Cleaning relevant data**

> a. **steam_data_1**


```{r}
#Cleaning dates
steam_data_1_cleaned_1 <- steam_data_1 %>%
  distinct(name, .keep_all = TRUE) %>%
  select(date, name, developer, user_reviews, all_reviews) %>%
  filter(!is.na(name),
         !name == "-",
         !is.na(developer),
         !date == "-",
         !str_detect(date, "\\w{3}", negate = TRUE)) %>%
  rename(game_name = name,
         release_date = date,
         reviews_all_time = all_reviews,
         reviews_30_days = user_reviews) %>%
  mutate(release_date = parse_date_time(release_date, orders = c("%b %d, %Y", 
                                                                 "%d %b, %Y",
                                                                 "%m/%d/%Y",
                                                                 "%Y/%m/%d",
                                                                 "%Y-%m-%d",
                                                                 "%d.%m.%Y",
                                                                 "%m.%d.%Y"))) %>%
  filter(!is.na(release_date))

#Cleaning developer
steam_data_1_cleaned_2 <- steam_data_1_cleaned_1 %>%
  mutate(d1 = str_split(developer,
                        ", (?!L(?i)t(?i)d(?i).?|L(?i)C(?i)C(?i).?|I(?i)n(?i)c(?i).?|L(?i).?L(?i).?C(?i).?|.dat|s. r. o.)")) %>%
  unnest_legacy(d1) %>%
  group_by(game_name) %>%
  mutate(temp_id = row_number()) %>%
  pivot_wider(names_from = temp_id,
              values_from = d1,
              names_prefix = "developer_") %>%
  select(-developer) %>%
  ungroup()
  
#Cleaning all_reviews
steam_data1_cleaned_3 <- steam_data_1_cleaned_2 %>%
  filter(str_detect(reviews_30_days, "%")) %>%
  mutate(reviews_all_time_pct = ifelse(!str_detect(reviews_all_time, "%"),
                                       NA,
                                       reviews_all_time),
         reviews_all_time_pct = ifelse(is.na(reviews_all_time_pct),
                                       reviews_30_days,
                                       reviews_all_time_pct)) %>%
  select(-reviews_30_days, -reviews_all_time) %>%
  mutate(reviews_all_time_pct = str_extract(reviews_all_time_pct, "[:digit:]+(?=%)"),
         reviews_all_time_pct = as.double(reviews_all_time_pct))
  

temp5 <- video_game_sales_1 %>%
  select(game, metascore, developer, release_date) %>%
  filter(!is.na(metascore)) %>%
  mutate(joined_game_name = str_replace_all(game, "[^[:alnum:] ]", " "),
         joined_game_name = str_to_lower(joined_game_name),
         temp_dev = str_split(developer,
                        ", (?!L(?i)t(?i)d(?i).?|L(?i)C(?i)C(?i).?|I(?i)n(?i)c(?i).?|L(?i).?L(?i).?C(?i).?|.dat|s. r. o.)")) %>%
  unnest_legacy(temp_dev) %>%
  group_by(release_date,game) %>%
  mutate(temp_id = row_number()) %>%
  pivot_wider(names_from = temp_id,
              values_from = temp_dev,
              names_prefix = "developer_") %>%
  ungroup() %>%
  select(-developer) %>%
  mutate(joined_dev = ifelse(is.na(developer_2),
                               developer_1,
                               str_c(developer_1, developer_2, sep = " ")),
         joined_dev = str_replace_all(joined_dev, "[^[:alnum:] ]", " "),
         joined_dev = str_to_lower(joined_dev),
         first_developer = ifelse(is.na(developer_1),
                                  developer_2,
                                  developer_1)) %>%
  select(game, metascore, joined_game_name, joined_dev, first_developer) %>%
  filter(!is.na(joined_dev))
  

temp4 <- video_game_sales_2 %>%
  select(Name, Critic_Score, Developer, NA_Sales) %>%
  filter(!is.na(Critic_Score)) %>%
  mutate(joined_game_name = str_replace_all(Name, "[^[:alnum:] ]", " "),
         joined_game_name = str_to_lower(joined_game_name),
         temp_dev = str_split(Developer,
                        ", (?!L(?i)t(?i)d(?i).?|L(?i)C(?i)C(?i).?|I(?i)n(?i)c(?i).?|L(?i).?L(?i).?C(?i).?|.dat|s. r. o.)")) %>%
  unnest_legacy(temp_dev) %>%
  group_by(Developer, Name, NA_Sales) %>%
  mutate(temp_id = row_number()) %>%
  pivot_wider(names_from = temp_id,
              values_from = temp_dev,
              names_prefix = "developer_") %>%
  ungroup() %>%
  select(-Developer) %>%
  mutate(joined_dev = ifelse(is.na(developer_2),
                               developer_1,
                               str_c(developer_1, developer_2, sep = " ")),
         joined_dev = str_replace_all(joined_dev, "[^[:alnum:] ]", " "),
         joined_dev = str_to_lower(joined_dev),
         first_developer = ifelse(is.na(developer_1),
                                  developer_2,
                                  developer_1)) %>%
  select(Name, Critic_Score, joined_game_name, joined_dev, first_developer) %>%
  filter(!is.na(joined_dev))



full_join_video_game_sales <- full_join(temp4, temp5, by = c("joined_game_name", "joined_dev")) %>%
  filter(!is.na(Critic_Score) | !is.na(metascore))

full_join_video_game_sales_critic <- full_join_video_game_sales %>%
  mutate(critic_score = rowMeans(full_join_video_game_sales[c('Critic_Score', 'metascore')], na.rm = TRUE)) %>%
  select(Name, critic_score, joined_game_name, joined_dev)

# Join with player score

steam_data1_joined_3 <- steam_data1_cleaned_3 %>%
  mutate(joined_game_name = str_replace_all(game_name, "[^[:alnum:] ]", " "),
         joined_game_name = str_to_lower(joined_game_name),
         joined_dev = ifelse(is.na(developer_2),
                               developer_1,
                               str_c(developer_1, developer_2, sep = " ")),
         joined_dev = str_replace_all(joined_dev, "[^[:alnum:] ]", " "),
         joined_dev = str_to_lower(joined_dev)) %>%
  select(release_date, game_name, joined_game_name, joined_dev, reviews_all_time_pct) %>%
  filter(!is.na(joined_dev))


#Fin
joined_critic_all_review <- left_join(full_join_video_game_sales_critic, steam_data1_joined_3, by = c("joined_game_name"))  %>%
  filter(!is.na(reviews_all_time_pct)) %>%
  select(Name, critic_score, reviews_all_time_pct) %>%
  rename("game_name" = Name,
         "avg_critic_score" = critic_score)


#ploting
joined_critic_all_review %>%
  ggplot() + 
  geom_point(aes(x = avg_critic_score,
               y = reviews_all_time_pct),
             size = 0.8,
             alpha = 0.5) +
  geom_smooth(aes(x = avg_critic_score,
                  y = reviews_all_time_pct),
              method = NULL)

```






## Question 4: Are there any relationship between Twitch's viewer and global sale of a game?

- cleaning twitch

```{r}
twitch_game_popularity_joined <- twitch_game_popularity %>%
  group_by(Game) %>%
  summarise(avg_all_time_viwers = mean(Avg_viewers)) %>%
  mutate(joined_game_name = str_replace_all(Game, "[^[:alnum:] ]", " "),
         joined_game_name = str_to_lower(joined_game_name)) %>%
  rename("game_name" = Game)



################################################################################################
video_game_sales2_joined <- video_game_sales_2 %>%
  group_by(Name, Developer) %>%
  summarise(sum_global_sales = sum(Global_Sales)) %>%
  mutate(joined_game_name = str_replace_all(Name, "[^[:alnum:] ]", " "),
         joined_game_name = str_to_lower(joined_game_name),
         sum_global_sales = sum_global_sales * 10) %>% # 100k
  select(Name, joined_game_name, sum_global_sales) %>%
  rename("game_name" = Name)  

#join 
joined_avg_viwer_global_sales <- inner_join(twitch_game_popularity_joined, video_game_sales2_joined, by = "game_name") %>%
  select(game_name, avg_all_time_viwers, sum_global_sales)  
 
#plot 1
joined_avg_viwer_global_sales %>%
  ggplot() + 
  geom_point(aes(x = sum_global_sales,
                 y = avg_all_time_viwers),
             size = 0.8,
             alpha = 0.5) +
  geom_smooth(aes(x = sum_global_sales,
                  y = avg_all_time_viwers),
              method = NULL) #+
 # ylim(0, 20000) +
  #xlim(0, 100)
  
#plot 2
joined_avg_viwer_global_sales %>%
  ggplot() + 
  geom_point(aes(x = sum_global_sales,
                 y = avg_all_time_viwers),
             size = 0.8,
             alpha = 0.5) +
  geom_smooth(aes(x = sum_global_sales,
                  y = avg_all_time_viwers),
              method = NULL) +
  ylim(0, 40000) +
  xlim(0, 100)

```




## Question 5: Can we have a model predicting global sales of a game using its genre, developer and critic score.

```{r}
#global sales
video_game_sales2_joinable_dev <- video_game_sales_2 %>%
  group_by(Name, Developer) %>%
  summarise(sum_global_sales = sum(Global_Sales)) %>%
  mutate(joined_game_name = str_replace_all(Name, "[^[:alnum:] ]", " "),
         joined_game_name = str_to_lower(joined_game_name),
         sum_global_sales = sum_global_sales * 10, #100k
         temp_dev = str_split(Developer,
                        ", (?!L(?i)t(?i)d(?i).?|L(?i)C(?i)C(?i).?|I(?i)n(?i)c(?i).?|L(?i).?L(?i).?C(?i).?|.dat|s. r. o.)")) %>%
  unnest_legacy(temp_dev) %>%
  group_by(Name, sum_global_sales) %>%
  mutate(temp_id = row_number()) %>%
  pivot_wider(names_from = temp_id,
              values_from = temp_dev,
              names_prefix = "developer_") %>%
  ungroup() %>%
  mutate(joined_dev = ifelse(is.na(developer_2),
                               developer_1,
                               str_c(developer_1, developer_2, sep = " ")),
         joined_dev = str_replace_all(joined_dev, "[^[:alnum:] ]", " "),
         joined_dev = str_to_lower(joined_dev),
         first_developer = ifelse(is.na(developer_1),
                                  developer_2,
                                  developer_1)) %>%
  select(Name, joined_game_name, joined_dev, sum_global_sales, first_developer) %>%
  filter(!is.na(joined_dev)) 
  
#Genre
steam_data1_joinable_first_genre <- steam_data_1_with_genres %>%
  select(game_name, joined_game_name, joined_dev, genre_1)

#Critic_score
full_join_video_game_sales_critic_joinable <- full_join_video_game_sales_critic %>%
  filter(!is.na(joined_game_name))

#fin
joined_q4 <- inner_join(video_game_sales2_joinable_dev, steam_data1_joinable_first_genre, by = "joined_game_name") %>%
  rename(joined_dev = joined_dev.x) %>%
  inner_join(full_join_video_game_sales_critic_joinable, by = c("joined_game_name", "joined_dev")) %>%
  unique() %>%
  select(game_name, sum_global_sales, first_developer, genre_1, critic_score)


#assigning artificial IDs to developer and genre
joined_q4_with_ids <- joined_q4 %>%
  group_by(genre_1) %>%
  mutate(genre_id = cur_group_id()) %>%
  group_by(first_developer) %>%
  mutate(developer_id = cur_group_id()) %>%
  ungroup()
  

#creating model
q4_mod <- cforest(sum_global_sales ~ developer_id + genre_id + critic_score, 
                       data = joined_q4_with_ids)

#add_prediction and residuals
q4_pred_resid <- joined_q4_with_ids %>% 
  add_predictions(q4_mod) %>%
  add_residuals(q4_mod)
  
#Justify model
q4_pred_resid %>%
  mutate(correct = ifelse(abs(resid) <= 0.5,
                          1,
                          0)) %>%
  summarize(mean(correct))

################################V222222222################################################################

#assigning artificial IDs to developer and genre
joined_q4_with_ids_2 <- joined_q4 %>%
  group_by(genre_1) %>%
  mutate(genre_id = cur_group_id()) %>%
  ungroup()
  

#creating model
q4_mod_2 <- cforest(sum_global_sales ~ genre_id + critic_score, 
                       data = joined_q4_with_ids_2)

#add_prediction and residuals
q4_pred_resid_2 <- joined_q4_with_ids_2 %>% 
  add_predictions(q4_mod_2) %>%
  add_residuals(q4_mod_2)
  
#Justify model
q4_pred_resid_2 %>%
  mutate(correct = ifelse(abs(resid) <= 1,
                          1,
                          0)) %>%
  summarize(mean(correct))

q4_pred_resid_2 %>%
  select(sum_global_sales, pred)
```














################################################Storage################################################


'''


#Cleaning dates
steam_data_1_cleaned_1 <- steam_data_1 %>%
  distinct(name, .keep_all = TRUE) %>%
  select(date, name, developer, user_reviews, all_reviews) %>%
  filter(!is.na(name),
         !name == "-",
         !is.na(developer),
         !date == "-",
         !str_detect(date, "\\w{3}", negate = TRUE)) %>%
  rename(game_name = name,
         release_date = date,
         reviews_all_time = all_reviews,
         reviews_30_days = user_reviews) %>%
  mutate(release_date = parse_date_time(release_date, orders = c("%b %d, %Y", 
                                                                 "%d %b, %Y",
                                                                 "%m/%d/%Y",
                                                                 "%Y/%m/%d",
                                                                 "%Y-%m-%d",
                                                                 "%d.%m.%Y",
                                                                 "%m.%d.%Y"))) %>%
  filter(!is.na(release_date))

#Cleaning developer
steam_data_1_cleaned_2 <- steam_data_1_cleaned_1 %>%
  mutate(d1 = str_split(developer,
                        ", (?!L(?i)t(?i)d(?i).?|L(?i)C(?i)C(?i).?|I(?i)n(?i)c(?i).?|L(?i).?L(?i).?C(?i).?|.dat|s. r. o.)")) %>%
  unnest_legacy(d1) %>%
  group_by(game_name) %>%
  mutate(temp_id = row_number()) %>%
  pivot_wider(names_from = temp_id,
              values_from = d1,
              names_prefix = "developer_") %>%
  select(-developer) %>%
  ungroup()
  
#Cleaning all_reviews
steam_data1_cleaned_3 <- steam_data_1_cleaned_2 %>%
  filter(str_detect(reviews_30_days, "%")) %>%
  mutate(reviews_all_time_pct = ifelse(!str_detect(reviews_all_time, "%"),
                                       NA,
                                       reviews_all_time),
         reviews_all_time_pct = ifelse(is.na(reviews_all_time_pct),
                                       reviews_30_days,
                                       reviews_all_time_pct)) %>%
  select(-reviews_30_days, -reviews_all_time) %>%
  mutate(reviews_all_time_pct = str_extract(reviews_all_time_pct, "[:digit:]+(?=%)"),
         reviews_all_time_pct = as.double(reviews_all_time_pct))
  



#joining all these information
test <- stringdist_inner_join(steam_data1_joinable_first_genre, video_game_sales2_joinable_dev, by = c("joined_game_name")) %>%

test2 <- test %>%
  select(Name, joined_game_name.y, genre_1, sum_global_sales, first_developer)  %>%
  rename("joined_game_name" = "joined_game_name.y") 

test3 <- stringdist_inner_join(test2, full_join_video_game_sales_critic_joinable, by = "joined_game_name")

video_game_sales2_joinable_dev <- video_game_sales_2 %>%
  group_by(Name) %>%
  summarise(sum_global_sales = sum(Global_Sales)) %>%
  mutate(joined_game_name = str_replace_all(Name, "[^[:alnum:] ]", " "),
         joined_game_name = str_to_lower(joined_game_name),
         sum_global_sales = sum_global_sales * 10, #100k
         temp_dev = str_split(Developer,
                        ", (?!L(?i)t(?i)d(?i).?|L(?i)C(?i)C(?i).?|I(?i)n(?i)c(?i).?|L(?i).?L(?i).?C(?i).?|.dat|s. r. o.)")) %>%
  unnest_legacy(temp_dev) %>%
  group_by(Name, sum_global_sales) %>%
  mutate(temp_id = row_number()) %>%
  pivot_wider(names_from = temp_id,
              values_from = temp_dev,
              names_prefix = "developer_") %>%
  ungroup() %>%
  mutate(joined_dev = ifelse(is.na(developer_2),
                               developer_1,
                               str_c(developer_1, developer_2, sep = " ")),
         joined_dev = str_replace_all(joined_dev, "[^[:alnum:] ]", " "),
         joined_dev = str_to_lower(joined_dev),
         first_developer = ifelse(is.na(developer_1),
                                  developer_2,
                                  developer_1)) %>%
  select(Name, joined_game_name, joined_dev, sum_global_sales, first_developer) %>%
  filter(!is.na(joined_dev)) 


